\section{Conclusion}
\label{sec:conclusion}
In this paper we have presented
\vmps, a framework providing programming support for the definition of
VM placement algorithms, execution support for their simulation at
large scales, as well as new means for their trace-based analysis.
\vmps enables, in particular, the investigation of placement
algorithms in the context of numerous and diverse real-world
scenarios. We have validated its accuracy of returned results by
comparing simulated and \textit{in-vivo} executions of the Entropy
strategy on top of 32~PMS and 192~VMs. We have illustrated the
relevancce of \vmps by evaluating and comparing algorithms
representative for three different classes of virtualization
environments: centralized, hierarchical and fully distributed
placement algorithms. We have also shown how \vmps facilitates the
implementation and evaluation of variants of placement algorithms. The
corresponding experiments have provided the first systematic results
comparing these algorithms in environments including up to one
thousand of nodes and ten thousands of VMs.

A beta-version of \vmps is available on a public git
repository\footnote{\url{http://beyondtheclouds.github.io/VMPlaceS/}}.
We are in touch with the \sg core developers in order to improve ou
code with the ultimate objective of adressing infrastructures up to
100K PMs and 1 Millions VMs. As future work, it would be valuable to add
additional dimensions in order to simulate other workload variations
stemming from network and HDD I/O changes. Finally,
we plan to provide a dedicated API to be able to
provision and remove VMs during the execution of a simulation.
% conference papers do not normally have an appendix
