\section{Future work}
\label{sec:future_work}

\subsection{Deeper validation with larger testbed}

Even if this article has demonstrated that the relational database used by Nova
could be replaced by a non relational key/value store, a more advanced
validation of this change is required and the question of which metrics to use
remains. On one hand, a larger deployment involving more geographical sites
would be more demonstrative, on the other hand the changes we introduced have
been have been motivated by more than overall scalabity, but also fault
tolerance and reduction of response times when processing API requests.

\subsection{Distributing the remaining services of OpenStack}

As introduced in section \ref{leveraging-openstack}, the other services
composing OpenStack are historically leveraging a relational database to store
their inner-states. As done with Nova, this relational database may be replaced
by a key/value data-store. Among the remaining services, the next candidate is
the image service Glance: as its images are already stored in fully distributed
cloud storage software (SWIFT), the next step to reach a fully distributed
functionning with Glance is to apply the same strategy that we did with Nova. On
the other  hand, the situation may be different with some other services:
Neutron works  with drivers that may be intented to work in a distributed way.
In such  situation alternatives have to be found.

\subsection{Locality aware objects in OpenStack}

Having a wan-wide infrastructure can be source of networking overheads: some
objects manipulated by OpenStack are subject to be manipulated by any service of
the deployed controllers, and by extension should be visible to any of the
controllers. On the other hand, some objects may benefit from a restrained
visibility: if a user has build an OpenStack project (tenant) that is based on
few sites, appart from data-replication there is no need for storing objects
related to this project on external sites. Restraining the storage of such
objects according to visibility rules would enable to save network bandwidth and
to settle policies for applications such as privacy and efficient data-
replication.
