\documentclass[a4paper,twoside]{article}

\usepackage{RR}
\usepackage{hyperref}
%\usepackage[frenchb]{babel}
%\usepackage[T1]{fontenc} % avec T1 comme option  d'encodage c'est ben mieux, surtout pour taper du français.
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath, amsthm}
\usepackage{stmaryrd}
\usepackage{lscape}

\usepackage{url} \urlstyle{sf}%
\usepackage{graphicx}%
\usepackage{subfigure}
\usepackage{listings}%

\lstset{%
  basicstyle=\scriptsize,%
  numbers=left,
  %columns=fullflexible,%
  language=XML,%
  %frame=shadowbox,
    frame=lbtr,%
  frameround=tttt,%
  tabsize=2,
  breaklines=true
}%
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,positioning}
\usepackage{array}
\usepackage{xspace}

\newcommand{\ie}[0]{{\em i.e.},\xspace}
\newcommand{\vs}[0]{{\em vs.}\xspace}
\newcommand{\eg}[0]{{\em e.g.},\xspace}
\newcommand{\etal}[0]{{\em et al.}\xspace}
\newcommand{\wrt}[0]{{\em w.r.t.}\xspace}
\newcommand{\aka}[0]{{\em a.k.a.}\xspace}

\sloppy

%%% FORMAT DOCUMENT

\def\textfraction{0}
\def\floatpagefraction{1}
\def\topnumber{3}
\def\bottomnumber{3}
\def\totalnumber{3}
\def\topfraction{1}
\def\bottomfraction{1}

%%.
\usepackage{bold-extra,graphicx,latexsym,mathrsfs,subfigure,xspace}

\usepackage{color}
\usepackage{array}
\usepackage{longtable}
\usepackage{calc}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{ifthen}

\usepackage{hyperref}

\newcolumntype{M}[1]{>{\raggedleft}m{#1}}
\newcommand{\discovery}{DISCOVERY\xspace}

%% CT %%
\newcommand{\ftodo}[2][\relax]  % \TODO[editor]{text} 
  {\ensuremath{{}^{\mbox{\tiny\bf #1}}}~\textbf{#2}}

\begin{document}

\RRNo{8779}
\RRdate{Sep 2015}

\RRprojet{Ascola, Asap, Avalon, Kerdata, Myriads}

% \author{Adrien L?bre\inst{1,3} \and Jonathan Pastor\inst{1,3} \and Marin Bertier \inst{2,3} \and Fr?d?ric Desprez\inst{3} \and Jonathan Rouzaud-Cornabas\inst{3} \and C?dric Tedeschi \inst{3,4}\and Paolo Anedda\inst{5} \and Gianluigi Zanetti\inst{5} 
% \and Ramon Nou\inst{6} \and Toni Cortes\inst{6} \and Etienne Riviere\inst{7} \and Thomas Ropars\inst{8}}
% \institute{LINA / Mines Nantes, France 
% \and IRISA / INSA de Rennes, France
% \and INRIA, France
% \and IRISA / Universit? de Rennes 1, France
% \and Center for Advanced Studies, Research and Development in Sardinia (CRS4), Italy
% \and Barcelona Supercomputing Center (BSC), Spain
% \and Universit? de Neuch?tel (UniNe), Switzerland
% \and Ecole Polytechnique F?d?rale de Lausanne (EPFL), Switzerland} 

%
% Title and Authors
%
\RRauthor{
A. Lebre\thanks[Inria]{Inria, France, Email: \url{FirstName.LastName@inria.fr}}\thanks[EMN]{Mines Nantes/LINA (UMR 6241), France.}%\inst{1} 
\and 
J. Pastor\thanksref{Inria}\thanksref{EMN} 
\and 
The Discovery Consortium\thanksref{Inria}  
}

\authorhead{A. Lebre et al.}

\RRtitle{L'initiative DISCOVERY - les infrastructures IaaS massivement distribuées comme solution aux principales limitations des plateformes de Cloud Computing actuelles}
\RRetitle{The DISCOVERY Initiative\\Overcoming Major Limitations of Traditional Server-Centric Clouds by Operating Massively Distributed IaaS Facilities}%\thanks{This report ....}}
\titlehead{The DISCOVERY Initiative}

%\RRnote {XXXX}

\RRkeyword{Locality-Based Utility Computing, 
Peer To Peer,
Self-*,
Sustainability,
Efficiency,
Future Internet.
}

\RRmotcle{Calcul utilitaire basé sur la localité, systèmes pair-à-pair, self-*, durabilité,
Internet du futur}

%
% Abstract
%
\RRabstract{

  {\small 

  Instead of the current trend consisting of building larger and
  larger data centers (DCs) in few strategic locations, the DISCOVERY
  initiative\footnote{\url{http://beyondtheclouds.github.io}}
 proposes to leverage any network point of presences (PoP, \ie a
  small or medium-sized network center) available through the
  Internet. The key idea is to demonstrate a widely distributed Cloud
  platform that can better match the geographical dispersal of users.
  This involves radical changes in the way resources are managed, but
  leveraging computing resources around the end-users will enable to
  deliver a new generation of highly efficient and sustainable Utility
  Computing (UC)
  platforms, thus providing a strong alternative to the actual Cloud
  model based on mega DCs (i.e. DCs composed of tens of thousands
  resources).

  Critical to the emergence of such distributed Cloud platforms is the
  availability of appropriate operating mechanisms. Although, some of
  protagonists of Cloud federations would argue that it might be
  possible to federate a significant number of micro-Clouds hosted on
  each PoP, we emphasize that federated approaches aim at delivering a
  brokering service in charge of interacting with several Cloud
  management systems, each of them being already deployed and operated
  independently by at least one administrator. In other words, current
  federated approaches do not target to operate, remotely, a
  significant amount of UC resources geographically distributed but
  only to use them. The main objective of DISCOVERY is to design,
  implement, demonstrate and promote a unified system in charge of
  turning a complex, extremely large-scale and widely distributed
  infrastructure into a collection of abstracted computing resources
  which is efficient, reliable, secure and friendly to operate and
  use.

  After presenting the DISCOVERY vision, we explain the different
  choices we made, in particular the choice of revising the OpenStack
  solution leveraging P2P mechanisms. We believe that such a strategy
  is promising considering the architecture complexity of such systems
  and the velocity of open-source initiatives.
}
}

\RRresume{

  {\small 

La tendance actuelle pour supporter la demande croissante d'informatique
utilitaire consiste à construire des centres de données de plus en plus grands,
dans un nombre limité de lieux stratégiques. Cette approche permet sans aucun
doute de satisfaire la demande actuelle tout en conservant une approche
centralisée de la gestion de ces ressources, mais elle reste loin de pouvoir
fournir des infrastructures répondant aux contraintes actuelles et futures en
termes d’efficacité, de juridiction ou encore de durabilité.  L’objectif de
l'initiative DISCOVERY\footnote{\url{http://beyondtheclouds.github.io}} est de
concevoir le \emph{LUC OS},  un système de gestion distribuée des ressources qui permettra de
tirer parti de n’importe quel n\oe ud réseau constituant la dorsale d’Internet
afin de fournir une nouvelle génération d’informatique utilitaire, plus apte à
prendre en compte la dispersion géographique des utilisateurs et leur demande
toujours croissante. 

Après avoir rappelé les objectifs de l'initiative DISCOVERY et expliqué
pourquoi les approches type fédération ne sont pas adaptées pour opérer une
infrastructure d'informatique utilitaire intégrée au réseau, nous présentons les
prémisses de notre système.  Nous expliquerons notamment pourquoi et comment
nous avons choisi de démarrer des travaux visant à revisiter la conception de
la solution Openstack. De notre point de vue, choisir d'appuyer nos travaux sur
cette solution est une stratégie judicieuse à la vue de la complexité des
systèmes de gestion des plateformes IaaS et de la vélocité des solutions
open-source. 
}
}

\URRennes
\makeRR

%%%

\input{introduction}

\input{design}

\input{openstack}


\input{conclusion}

%
% Section: Acknowledgment
%
\section*{Acknowledgments}

Since July 2015, the Discovery initiative is mainly supported through the Inria Project Labs program and the I/O labs, a joint lab between Inria and Orange Labs.
Further information at \href{http://www.inria.fr/en/research/research-fields/inria-project-labs}{http://www.inria.fr/en/research/research-fields/inria-project-labs}
%
% Bibliography
%



\bibliographystyle{abbrv}
\bibliography{main}
\end{document}
