    Most current infrastructures for cloud computing leverage static
    and greedy policies for the placement of virtual machines. Such
    policies impede the optimal allocation of resources and the
    satisfaction of operational guarantees like service-level
    agreements. In recent years, more dynamic and often more efficient
    policies based, \eg on consolidation and load balancing
    techniques, have been developed and investigated. New policies are
    typically evaluated either using testbeds or \emph{in-vivo}
    experiments. However, due to the underlying complexity of cloud
    infrastructures, testbeds typically have to be tailored to
    specific restricted configurations and experiments on real
    infrastructures are necessarily of limited scale.

    In this article, we propose \vmps, a dedicated simulation
    framework to perform in-depth investigations of VM placement
    algorithms and compare them in a fair way. This framework, built
    on top of the \sg simulation platform, notably provides
    programming support to easy the implementation of placement
    algorithms and runtime support dedicated to load injection and
    execution trace analysis. \vmps supports the simulation of a large
    set of real-world configurations, while allowing researchers to
    conduct experiments at large scales. We also report on a
    validation of our framework by implementing and investigating
    representative algorithms for three classes of placement
    algorithms: centralized, hierarchical and fully-distributed ones.
